From Reversible Programs to \\ Univalent Universes and Back

### 2021-04-19 Pi+/paper/discussion.tex
Some more outline

\section{Univalent Subuniverses}~\label{sec:univalent}

>>>>

\section{Discussion \& Related Work}~\label{sec:discussion}

Algebraic theories, 2-algebraic theories, Syntax of Coherence (Yanofsky)

Higher order rewriting theory in constructive type theory.

Free monoids, free commutative monoids, normalisation of monoids.

Coherence problems in type theory, coherence via Well-Foundedness.

Computational group theory (in HoTT?)

Presentation of the free symmetric monoidal groupoid on one generator, proof of Mac Lane's coherence theorem in HoTT.

Alternatively, we can describe them using HITs, prove they have the universal property and hence equivalent.
The full Pi is FSMG 1, and the normalised fragment of Pi is M1.

Applications of FSMG and history of the coherence theorems.

Other proofs of coherence theorems, Joyal-Street.

Pi has other extensions (fractional/negative/recursive types).
What are the free X monoidal structures they're describing?

Using our presentation of $S_{n}$, we can construct the Eilenberg-Maclane space (using a HIT) $K(S_{n},1)$. Then, it
should be true that $\UFin \eqv \sqcup_{n:\Nat} K(S_{n},1)$. This is future work.

Other applications of symmetric groups.

Actions of symmetric groups, permutation groupoids.

### 2021-04-19 Pi+/paper/equivalence.tex
Work
Fix build
Some more outline

\section{Discussion \& Related Work}~\label{sec:discussion}

>>>>

\section{Equivalence between \texorpdfstring{$\PiPlusLang$}{Pi} and \texorpdfstring{$\UFin$}{UFin}}~\label{sec:equivalence}

First, we normalise $\PiPlusLang$ to $\PiHatLang$, and show that they are equivalent.

Then we establish the completeness of $\PiHatLang$ with respect to $\UFin$.

We use this to establish completeness for $\PiPlusLang$.

Finally, we show how to translate $\PiLang$ programs to $\PiPlusLang$ programs.

### 2021-04-19 Pi+/paper/finite.tex
Some more outline

In this section, we describe the algebraic structure of the groupoid of finite types by characterising its paths.

@@

>>>>

In this section, we describe the algebraic structure of the groupoid of finite types, and give a computable presentation
for it.

@@

\subsection{Symmetric Monoidal structure}

$\UFin$ is a symmetric monoidal groupoid with unit and tensor given by

\begin{definition}
  \begin{align*}
    I & \defeq \Fin[0] \\
    X \otimes Y & \defeq X \sqcup Y
  \end{align*}
\end{definition}

with unitors, associator, and braiding satisfying Mac Lane's triangle, pentagon, and hexagon coherence laws, and
symmetry. It is the free symmetric monoidal groupoid on one generator.
